### 2012-11-13 paper.tex
done mantri

>>>>

The first targeted solution for Mantri is restarting the task. There are 2 forms of restart that Mantri uses. The first form is to kill the existing running task and to restart it somewhere else. The other form is to duplicate the existing task and run it elsewhere. The restart solution kicks in only when there is a high chance that the time taken for the new task to complete is smaller than the time remaining for the current task to complete. However, restarting a task would require computational resources, this is only done when there are idle worker machines. When more spare jobs are available, Mantri will then schedule duplicates a little more aggressively.\\

The second targeted solution is to place tasks in such a way that it is aware of the network environment around it. As shown in section $1.1.3$, \emph{reduce} tasks will first have to read the intermediate files generated by the various \emph{map} tasks. If a server rack has too many \emph{reduce} tasks, it's incoming network would very likely be congested, and this would have a detrimental effect on all the \emph{reduce} tasks running on the rack. Using Mantri, the programs that manage the tasks will locate the task on the worker machines based while trying to reduce the load on the network, and try to prevent the various tasks from mutually interfering. It has an algorithm that figures out which is the optimal location to place all the tasks based on network bandwidth, in such a way such that the maximum data transfer time is minimized.\\

The third targeted solution is to avoid recomputations. As mentioned in the earlier section on MapReduce, the MapReduce library will store the output of \emph{map} tasks on local storage, and hence when the machine fails, the output is gone, and recomputation would need to be redone. In this case, Mantri will replicated the output data in tasks whose recomputation costs are higher than the replication costs. The recomputation costs is calculated by taking the product of the probability that the machine will fail with the estimated time for the task to be recomputed. The estimated time to recompute is calculated taking into account that the input is lost as well. For example, in a \emph{reduce} task, which takes in a large number of input, the estimated time to recomputate would be higher as recomputing the intermediate data to feed to the \emph{reduce} task as input data will stall the operation as a whole. In essence, the output is replicated when $1)$ the cummulative costs of not replicated consecutive task increases, or $2)$ when the machines used are really unstable, or $3)$ when the output is really small such that the cost of replication is neglible. However, it is worht noting that Mantri will enforce a limit on the amount of data to be replicated to up to 10\%. Each job will have a token proportional to the data processed, and if the cost benefit check is satisfactory for replication, the replication is done only when there are sufficient tokens available, and the tokens are deducted on replication of data.\\

In addition, the task ordering by Mantri will take into account the size of each task. It will schedule the longer tasks first, and run the smaller tasks last, so that it is at most 33\% slower than the optimal schedule, which is NP-hard to compute.\\

The tasks will also estimate the time remaining via the following equation.

$time_{remaining} = time_{elapsed} * \frac{data}{data_{read}} + time_{wrapup}$

Mantri uses a moving average, and in order to handle lost reports, if a task has not reported for some time, $time_{remaining}$ is automatically increased, with the assumption that no progress has been made.
